%! suppress = MissingImport
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[8pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------
\ifdefined\generated
\else
\newcommand{\generated}{manually}
\fi

\newcommand{\linebreaksmall}{\vspace{2mm}}
\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Daniel}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Draper}}}}} % Last name
	
	\vspace{6pt}
	
	{\large Senior Full-Stack Machine Learning Engineer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{9}{Karlsruhe, Germany}\\
	\icon{Phone}{9}{+49 176 95767859}\\
	\icon{At}{9}{\color{blue}{\href{mailto:germandrummer92@gmail.com}{germandrummer92@gmail.com}}}\\
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	%\icon{Globe}{12}{\href{https://alyx.vance.me}{alyx.vance.me}}\\
	\icon{Github}{9}{\color{blue}{\href{https://github.com/germandrummer92}{github.com/germandrummer92}}}\\
	\icon{Twitter}{9}{\color{blue}{\href{https://twitter.com/@germandrummer92}{@germandrummer92}}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	I am a Software Engineer with >5 years of experience working in the full software stack, developing SaaS products.
	My work has entailed \textbf{Mobile Applications}, \textbf{Web-Frontends}, \textbf{RESTful backend APIs} as well as full Computer Vision \textbf{Machine Learning Models} including deployment in the cloud (\textbf{Kubernetes}).
	Software Craftsmanship is my passion: I always aim for delivering clean, tested and readable software.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{Python}{100}
		\baritem{Tensorflow/Keras}{70}
		\baritem{TypeScript}{80}
		\baritem{Node.js/express}{70}
		\baritem{Vue.js}{60}
		\baritem{MongoDB}{70}
		\baritem{Cloud/Kubernetes}{40}
		\baritem{Kotlin}{40}
		\baritem{Swift}{40}
	\end{barchart}
\end{minipage}

%\begin{center}
%	\bubbles{5/Eclipse, 6/git, 4/Office, 3/Inkscape, 3/Blender}
%\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{2019 -- Current}
		{Senior full-stack machine learning engineer}
		{understand.ai gmbH}
		{Worked on entire tool chain of the understand.ai annotation product: Producing ground-truth annotations for perception stacks of autonomous driving using automation. Frontend-development using vue.js, opengl with typescript. Backend development using express on top of a MongoDB non-relational database. Developed computer vision machine learning models using python, tensorflow, keras. Data engineering using numpy, open3d, scipy. Deployment of models and batch data processing jobs on Kubernetes.
		\linebreaksmall \\ \texttt{Python}\slashsep\texttt{TypeScript}\slashsep\texttt{Vue.js}\slashsep\texttt{Node.js}\slashsep\texttt{MongoDB}\slashsep\texttt{Kubernetes}\slashsep\texttt{Tensorflow/Keras}} \linebreaksmall
	\entry
		{2017 -- 2019}
		{Full-stack mobile applications engineer}
		{LogMeIn Inc.}
		{Full-Stack Software Engineer. Worked on platform team managing backend services related to the real-time-communication (rtc) of \textit{GoToMeeting}. Worked on the native \textit{GoToMeeting}, \textit{GoToMeeting Messenger} iOS and android applications. Part of the internationally distributed team that developed a new rtc-enabled react-native cross-platform application \textit{GoToConnect} from scratch.
		\linebreaksmall \\ \texttt{Swift}\slashsep\texttt{Kotlin}\slashsep\texttt{TypeScript}\slashsep\texttt{iOS}\slashsep\texttt{Android}} \linebreaksmall
	\entry
		{2015 -- 2017\\\footnotesize{part-time}}
		{Working student software engineering}
		{1\&1 Telecommunications SE}
		{Worked on network/data center monitoring tools: Alert management for network operation engineers to get early alerts on potential incidents in 1\&1s own data centers according to aggregated network statistics. Simple Network Management Protocol (SNMP) querying/aggregation for datacenter-network devices (routers etc.).
		\linebreaksmall \\ \texttt{Java}\slashsep\texttt{Python}\slashsep\texttt{Ansible}\slashsep\texttt{Docker}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2015 -- 2017}
		{Computer Science, Msc}
		{Karlsruhe Institute of Technology}
		{Focus on machine learning/artificial intelligence classes, especially in the automatic speech recognition and natural language processing realms. Final Thesis: Online neural-network-based Language Identification. Available on \color{blue}{\href{https://github.com/Germandrummer92/master-thesis}{github}}.}
	\entry
		{2012 -- 2015}
		{Computer Science, Bsc}
		{Karlsruhe Institute of Technology}
		{Thesis: A Theory of Refinement of Cyber-Physical-Systems into Implementations. Available on \color{blue}{\href{https://github.com/Germandrummer92/Bachelor-Thesis}{github}}.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	\newline
	\textbf{German} - native\\
	\textbf{English} - near native\\


\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
	I love playing percussion/timpani in symphonic orchestras.
	Playing in 3+ different orchestras:
	\begin{itemize}
	  \item{Collegium Musicum KIT}
	  \item{Philharmonie KIT}
	  \item{Sinfonieorchester KIT}
	  \end{itemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Non profit}
	
	2017 - Orangutan Foundation International - Construction Volunteer in Pangkalan Bun, Indonesia.
	Helped build wooden walkways and shelters in old zoo.
\end{minipage}
\mbox{}
\vfill
\begin{minipage}[t]{1.0\textwidth}
\centering{\footnotesize{This document was generated \generated~on \today. Source Code available on \color{blue}{\href{https://github.com/Germandrummer92/resume}{github}}.}}

\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
